---
geometry: margin=1in
---

# Midterm study guide: R only

*STS198: Spring 2017*

You should be familiar with all the functions we have covered in
class:

  * ls()
  * head()
  * tail()
  * length()
  * unique()
  * table()
  * sort()
  * summary()
  * which()
  * c()
  * paste()
  * "==" (logical comparison)
  * "[" (subset)
  * names(), colnames(), rownames()
  * subset()
  * !=
  * \>= 
  * <= 
  * \&
  * |
  * tapply()
  * ggplot()
	- geom_histogram()
	- geom_boxplot()
	- geom_points()
	- geom_density()
	- geom_violin()
	- geom_bar()
	- geom_smooth()

### You should be able to answer questions such as:

```{r}
x = c(1,3,5,9)

```

  * What does \texttt{x[4]} equal?
  
  * How many elements are in the output of \texttt{x == 5}?
  
  * What data type is \texttt{x}? (numeric, logical, character)
  
  * What is the result of \texttt{x[x >= 5]}?
  
```{r}
str(mtcars)  
head(mtcars)
```

  * What is the expected length of \texttt{mtcars\$cyl}?

  * How many rows are there in \texttt{mtcars}? Columns?
  
```{r}
table(mtcars$cyl)
```
  * How many rows are in the result of \texttt{subset(mtcars, cyl ==
    4)}? How many columns?

```{r, echo=FALSE, fig.width=4, fig.height=4, fig.cap="What code produced me?"}
library(ggplot2)
ggplot(mtcars, aes(x = factor(cyl))) +
    geom_bar() +
    coord_flip()

```

  * Which code chunk produced the above plot?
  
```{r eval=FALSE}

ggplot(mtcars, aes(x = factor(cyl))) +
    geom_bar() +
    coord_flip()

ggplot(mtcars, aes(x = factor(cyl),
                   fill = factor(am))) +
    geom_bar() +
    coord_flip()

ggplot(mtcars, aes(x = factor(cyl))) +
    geom_bar() 

ggplot(mtcars, aes(x = cyl)) +
    geom_point(stat = "count")

```

```{r}
table(mtcars$gear)
```

  * \texttt{sort(table(mtcars\$gear), decreasing = FALSE)[1]} returns?

  * \texttt{sort(table(mtcars\$gear), decreasing = TRUE)[1]} returns?
  
  * Do \texttt{subset(mtcars, cyl == 4 | cyl == 6)} and \texttt{subset(mtcars,
    cyl \%in\% c(4,6))} return the same thing?
	
  * Do \texttt{subset(mtcars, cyl == 6)} and \texttt{subset(mtcars,
    cyl == "6")} return the same thing?
	
